Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-07-03 ms.tex
got rid of clear page.
finished the statistical comparison section.

\clearpage

@@

Figure \ref{fig:tserPC} shows the time series of the first two principal components.
We highlight the quiescent periods also discussed in \citet{kawahara2013starspots}, \citet{vanWerkhoven2014} and \citet{croll2015starspots}.
The first principal component largely tracks closely with the dot product of the average light curve ($A'$).
The quiescent periods show up as 14 to 36 day long intervals of low amplitude events.
The second principal component shows some sinusoidal behavior at a $\sim$500 day period, indicating that the large particles may be evolving.
However, the timescales are much longer than dynamical and sublimation times for this system.

@@

@@

In Figure \ref{fig:ampPeriodogram} we show the periodogram of the principal components.
The peaks at 0.654 days in both the first and second principal components are the same as the orbital period and are the same as the sampling interval of the time series.
The first component, corresponding to the transit depth, has peaks at 22.9, 153 and 750 days.
The 22.9 day peak is consistent with the \citet{kawahara2013starspots} and \citet{croll2015starspots} that shows amplitudes are anti-correlated with stellar flux.
As suggested in \citet{kawahara2013starspots}, the anti-correlation points to a physical mechanism for the disintegration - such as magnetic activity or high energy flux associated with spots causing disintegration on the planet.
The second principal component's periodogram has a strong peak at 491 days.
This singly-peaked periodogram implies that PC$_2$ is nearly sinusoidal.
As shown in Figure \ref{fig:pcaVectorsComp}, the second principal component resembles models with larger dust grains, so the dust grain sizes could be evolving on long-term 491-day timescales.
This is much longer than the dynamical and sublimation times of the system, so there is no obvious mechanism for the dust grain size evolution.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pc1_periodogram.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pc2_periodogram.pdf}
\caption{Periodograms of the principal component time series shown in Figure \ref{fig:tserPC}, with peaks marked with red circles.
The first peak at 0.654 days for both principal components is the orbital period, which is the sampling time for these time series.
The PC$_1$ also peaks at 153 and 750 days, likely because of the intervals of low disintegration activity.
The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.
The second principal components shows one dominant peak at 491 days, in addition to the 0.654 orbital period.}\label{fig:ampPeriodogram}
\end{centering}
\end{figure*}

@@

\subsection{Statistical Analysis of Ground-based Photometry}\label{sec:statistics}
We calculate and evalute the Kepler transit amplitudes to better understand the long-term behavior of \sha's disintegration.
We take the histogram of transit amplitudes as measured by the Kepler light curves (shown in Figure \ref{fig:histoPhot}) and compare these to the ground-based photometry from \citet{schlawin2016kic1255} and this work.
The histogram of secondary eclipse amplitudes from the Kepler light curves is also shown in \ref{fig:histoPhot}.
The intrinsic astrophysical variation of the planet disintegration is convolved by this photometric scatter in the data.
We compare the distribution of amplitudes from \citet{schlawin2016kic1255} from the Kepler long cadence data from 2009 to 2013.
A Kolmogorov-Smirnov test gives a p value of 0.001 of the null hypothesis that the \citet{schlawin2016kic1255} results are drawn from the same distribution as the Kepler Long Cadence data.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amp_distributions_comparison.pdf}
\caption{Normalized frequency of 4 different transit amplitude distributions: 1) all of the Kepler Long Cadence data from 2009 to 2013, 2) the secondary eclipse amplitudes from the Kepler spacecraft over this same period, 3) the 8 night ground-based IRTF campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 4) the 5 night Kuiper observatory campaign in the summer of 2016.
The \citet{schlawin2016kic1255} (S16) events give a KS-test p value of 0.001 of the null hypothesis when comparing to the Kepler data.
In contrast, the 2016 photometric results in this work are consistent with the Kepler Long Cadence data, giving a  p value of 0.5 of the null hypothesis.
This indicates that the transit depths are back to normal and there is no slowdown of disintegration activity over time.}\label{fig:histoPhot}
\end{centering}
\end{figure*}

>>>>

@@

@@

Figure \ref{fig:tserPC} shows the time series of the first two principal components.
We highlight the quiescent periods, which are also discussed in \citet{kawahara2013starspots}, \citet{vanWerkhoven2014} and \citet{croll2015starspots}.
The first principal component largely tracks closely with the dot product of the average light curve ($A'$).
The quiescent periods show up as 14 to 36 day long intervals of low amplitude events.
The second principal component shows some sinusoidal behavior at a $\sim$500 day period, indicating that the large particles may be evolving.
However, the timescales are much longer than dynamical and sublimation times for this system.

@@

In Figure \ref{fig:ampPeriodogram} we show the periodogram of the principal components.
The peaks at 0.654 days in both the first and second principal components are the same as the orbital period, which determines the the sampling cadence of the time series of amplitudes and principal components.
The first component, corresponding to the transit depth, has peaks at 22.9, 153 and 750 days.
The 22.9 day peak is consistent with the \citet{kawahara2013starspots} and \citet{croll2015starspots} that shows amplitudes are anti-correlated with stellar flux.
As suggested in \citet{kawahara2013starspots}, the anti-correlation points to a physical mechanism for the disintegration - such as magnetic activity or high energy flux associated with spots causing disintegration on the planet.
The second principal component's periodogram has a strong peak at 491 days.
This singly-peaked periodogram implies that PC$_2$ is nearly sinusoidal.
As shown in Figure \ref{fig:pcaVectorsComp}, the second principal component resembles models with larger dust grains, so the dust grain sizes could be evolving on long-term 491-day timescales.
This is much longer than the dynamical and sublimation times of the system, so there is no obvious mechanism for the dust grain size evolution.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pc1_periodogram.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pc2_periodogram.pdf}
\caption{Periodograms of the principal component time series shown in Figure \ref{fig:tserPC}, with peaks marked with red circles.
The first peak at 0.654 days for both principal components is the orbital period, which is the sampling cadence of the principal components' time series.
PC$_1$ also peaks at 22.9, 153 and 750 days.
The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.
The second principal components shows one dominant peak at 491 days, in addition to the 0.654 orbital period, indicating possible long term evolution of the dust particle sizes.}\label{fig:ampPeriodogram}
\end{centering}
\end{figure*}

@@

\subsection{Statistical Analysis of Ground-based Photometry}\label{sec:statistics}
We calculate and evaluate the Kepler transit amplitudes to compare to ground-based results and to understand the long-term behavior of \sha's disintegration.
We take the histogram of transit amplitudes as measured by the Kepler light curves (shown in Figure \ref{fig:histoPhot}) and compare these to the ground-based photometry from \citet{schlawin2016kic1255} and this work.
The histogram of secondary eclipse amplitudes from the Kepler light curves is also shown in \ref{fig:histoPhot}, which shows the spread due to photon noise.
The intrinsic astrophysical variation of the planet disintegration is convolved by this photometric scatter in the data.

We compare the distribution of amplitudes from \citet{schlawin2016kic1255} from the Kepler long cadence data from 2009 to 2013.
A Kolmogorov-Smirnov (KS) test gives a p value of 0.001 of the null hypothesis that the \citet{schlawin2016kic1255} results are drawn from the same distribution as the Kepler Long Cadence data.
This indicated a possible slowdown of disintegration activity.
However, the distribution from this work taken in 2016 shows consistency with the Kepler histogram, with the KS test p value of 0.5 of the null hypothesis. 
We therefore conclude that the disintegration activity is stochastic with no long-term trend measurable from ground-based photometry.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amp_distributions_comparison.pdf}
\caption{Normalized frequency of 4 different transit amplitude distributions: 1) all of the Kepler Long Cadence data from 2009 to 2013, 2) the secondary eclipse amplitudes from the Kepler spacecraft over this same period, 3) the 8 night ground-based IRTF campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 4) the 5 night Kuiper observatory campaign in the summer of 2016.
The \citet{schlawin2016kic1255} (S16) events give a KS-test p value of 0.001 when comparing to the Kepler data.
In contrast, the 2016 photometric results in this work are consistent with the Kepler Long Cadence data, giving a  p value of 0.5.
This indicates that the transit depths are back to normal and there is no slowdown of disintegration activity over time.}\label{fig:histoPhot}
\end{centering}
\end{figure*}
